An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-19 Paper.tex
Edit proof of oos bootstrap normality
This commit makes some extensive changes to the oos bootstrap normality
result; I change the conditions to better match West's argument, and I
spell out most of the details of the proof.

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (v_t - x_t'\beta_0)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{2}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (v_t -
  x_t'\beta_0) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} - 
  x_t\beta_0)^2 - (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
\end{equation}

@@

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\beta_0$ and produce
$\hat{\varepsilon}_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06}, these conditions are ensured if $v_t$ is another
forecast of $y_{t+1}$ based on a fixed length rolling window.
Theorem~\ref{res:1} presents the details of this result.  The
assumptions required are essentially the same in existing papers
(e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).  Please see the
original papers for a discussion of these assumptions.

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
    $\bar f(\beta_0)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_0) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\beta_0) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    and $\E h_{s}(\beta_0) = 0$ for all $s$.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and twice continuously
    differentiable with bounded second derivative in an open
    neighborhood $N$ of $\beta_0$.  Also, $\E \sup_{\beta \in N}
    |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in N} |\frac{\partial
      \psi_t(\beta)}{\partial \beta'}|^r$ are uniformly bounded ($r$ is
    defined below).
  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
      uniform mixing processes, $r = 2$ is also allowed as long as
      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
      integrable.}
  \item The sequence $\psi_1^{*},\dots,\psi_T^{*}$ is generated by the
    moving blocks, circular blocks, or stationary bootstrap with block
    lengths drawn from the geometric distribution.  The (expected)
    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T h_t^* = 0$ a.s.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

\begin{rem}
  \citet{Mcc:00} proves asymptotic normality under weaker smoothness
  condtions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
  must be continuously differentiable.  It may be possible to extend
  Theorem~\ref{res:3} to those weaker conditions, but the current
  proof relies on a theorem of \citepos{JoD:00} establishing the
  consistency of \hac\ estimators which requires differentiability of
  the observations.  Extending \citepos{JoD:00} result to
  nondifferentiable functions should be possible, but is beyond the
  scope of this paper.
\end{rem}

@@

\begin{proof}[Proof of Theorem~\ref{res:3}] Expand $\E^{*}
  f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T+1}$ to get
  \begin{equation}
    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T+1})) =
    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
    \big[f_t^{*}(\hat{\beta}_{T+1}) - \bar{f}(\hat{\beta}_{T+1}) +
    F^{*} B^{*} a_t h_t^{*} \big] + o_{p^{*}},
  \end{equation}
  with $a_t = \sum_{s=\max\{t,R\}}^T \tfrac1s$.  The proof is the same
  as in \citet[Theorem 2.3.1]{Mcc:00}.  Note that $F^{*} = \hat{F} +
  o_{p}(1) = F + o_p(1)$ and $B^{*} = B + o_{p}(1)$.  The result then
  follows from Lemma~\ref{res:a3}.
\end{proof}

@@

\begin{lema}\label{res:a3}
  Suppose the conditions of Theorem~\ref{res:3} hold and let
  \[\psi_t^{*}(\beta) = 
  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)}.\]
  Then
  \begin{equation}\label{eq:1}
    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}(\hat\beta_T)
    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}(\beta_0)
    \leq x \Big] \Big| > \epsilon \Big] \to 0
  \end{equation}
  for all positive $\epsilon$.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a3}]
  Note that both $\psi_t(\beta_0)$ and $\psi_t^*(\hat\beta_T)$ satisfy
  \clt s, (\citealp[Theorem~2]{Jon:97} and
  \citealp[Theorem~1]{Cal:11d}) so it suffices to prove that
  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^*( \hat
  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t(
  \beta_0 ) \Big) \to^p 0. \]
  I will prove this result for the Circular Block Bootstrap
  \citep{PoR:92}---the proof for other block bootstraps is similar and
  follows as in \cite{Cal:11d}.

@@

  The first term of \eqref{eq:6} can be shown to converge in
  probability to $(1/P) \var \sum_{t=R+1}^T \psi_t( \beta_0 )$
  by Theorem 2.2 of \citet{JoD:00}.  Most of the necessary conditions
  hold by assumption and it suffices to prove their condition (2.9)
  holds, namely that
  \begin{equation}\label{eq:2}
    \sup_{\beta \in N} \Bigg\lVert \tfrac{1}{T} \sum_{t=1}^T e^{i \xi t/b} 
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} -
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
    \Bigg\rVert_2 \to 0
  \end{equation}
  for all $i$, $j$, and $\xi$.  Now, for any fixed $\beta \in N$,
  \begin{equation*}
    \tfrac{1}{T} \sum_{t=1}^T \cos( \xi t / b )
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
    \to^p 0
  \end{equation*}
  and
  \begin{equation*}
    \tfrac{1}{T} \sum_{t=1}^T \sin( \xi t / b )
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
    \to^p 0
  \end{equation*}
  by a mixingale \lln\ \citep{Dav:93}.\footnote{Remember that \ned\
    processes are also mixingales.  See, for example, \citet[Section
    17.2]{Dav:94}.}  Convergence in $L_2$ for each $\beta \in N$ then
  follows from the existence of the $r$th moment and uniform
  convergence is a consequence of the bounded second derivative of
  $\psi_t$.

@@

\begin{lema}\label{res:a5}
  If the conditions of Theorem~\ref{res:3} hold\footnote{The
    assumptions governing $\hat{\beta}_t^{*}$ are unnecessary.} then
  \begin{equation}
    \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
  \end{equation}
  with $\Omega$ given in \citet[Theorem 2.3.1]{Mcc:00}.
\end{lema}
\begin{proof}[Proof of Lemma~\ref{res:a5}]
  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}, using
  the previous results in this appendix as substitutes where the
  original proof requires stronger moment or weak dependence
  conditions.
\end{proof}

>>>>

\newcommand{\osum}[1]{\sum_{#1=R+1}^T}
\newcommand{\oavg}[1]{\tfrac{1}{P} \osum{#1}}
\newcommand{\oclt}[1]{\tfrac{1}{\sqrt{P}} \osum{#1}}

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\beta_0)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{2}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\beta_0) = \oclt{t} \Big[(y_{t+1} - 
  x_t\beta_0)^2 - (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
\end{equation}

@@

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\beta_0$ and produce
$\hat{\varepsilon}_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06}, these conditions are ensured if $v_t$ is another
forecast of $y_{t+1}$ based on a fixed length rolling window.
Theorem~\ref{res:1} presents the details of this result.  The
assumptions required are essentially the same in existing papers
(e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).  Please see the
original papers for a discussion of these assumptions.

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
    $\bar f(\beta_0)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \osum{t} g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_0) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\beta_0) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    and $\E h_{s}(\beta_0) = 0$ for all $s$.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and twice continuously
    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
    uniformly bounded ($r$ is defined below), and there exists a
    sequence of random variables $m_t$ such that $\sup_{i,\beta \in N}
    |\tfrac{\partial^2}{\partial \beta \partial \beta'}
    \psi_{it}(\beta)| \leq m_t$ almost surely and $\E m_t^2$ is
    uniformly finite.
  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
      uniform mixing processes, $r = 2$ is also allowed as long as
      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
      integrable.}
  \item The sequence $\psi_1^{*},\dots,\psi_T^{*}$ is generated by the
    moving blocks, circular blocks, or stationary bootstrap with block
    lengths drawn from the geometric distribution.  The (expected)
    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T h_t^* = 0$ a.s.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

\begin{rem}
  \citet{Mcc:00} proves asymptotic normality under weaker smoothness
  conditions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
  must be continuously differentiable.  It may be possible to extend
  Theorem~\ref{res:3} to those weaker conditions, but the current
  proof relies on a theorem of \citepos{JoD:00} establishing the
  consistency of \hac\ estimators which requires differentiability of
  the observations.  Extending \citepos{JoD:00} result to
  nondifferentiable functions should be possible, but is beyond the
  scope of this paper.
\end{rem}

@@

\newcommand{\WesA}{\oclt{t} (\nabla
  f_t^*(\hat\beta_{T}) - F^*) B^* H_t^*}
\newcommand{\WesB}{\tfrac{1}{\sqrt{P}} F^* \osum{t} (B_t^* -
  B^*) H_t^*}
\newcommand{\WesC}{\oclt{t} (\nabla
  f_t^*(\hat\beta_{T}) - F^*) (B_t^* - B^*) H_t^*}
\begin{proof}[Proof of Theorem~\ref{res:3}]
  Expand $\E^{*} f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T}$
  to get
  \begin{align*}
    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T})) &= \oclt{t}
    f_t^{*}(\hat{\beta}_{T}) - \bar{f}(\hat{\beta}_{T}) +
    F^{*} B^{*} \oclt{t} H_t^* \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t^*
  \end{align*}
  where (as in \citealp{Wes:96}) the $i$th element of $w_t^*$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_T)'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
    f_{it}^*(\tilde\beta_{it}^*) \Big]
    (\hat\beta_t^* - \hat\beta_T)
  \end{equation*}
  and each $\tilde\beta_{it}^*$ lies between $\hat\beta_t^*$ and
  $\hat\beta_T$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
  identical to West's, using our Lemma~\ref{res:a2} in place of his
  Lemma A3.  Then
  \begin{gather}
    \WesA \to^{p^*} 0 \label{eq:7} \\
    \WesB \to^{p^*} 0 \label{eq:9} \\
  \intertext{and}
    \WesC \to^{p^*} 0 \label{eq:10}
  \end{gather}
  from Lemma~\ref{res:a4} and the result follows from Lemma~\ref{res:a3}.
\end{proof}

@@

\begin{lema}\label{res:a4}
  Under the conditions of Theorem~\ref{res:3}, \eqref{eq:7},
  \eqref{eq:9}, and \eqref{eq:10} hold.
\end{lema}
\noindent For each of these results, I will present the proof for the
recursive window and the circular block bootstrap only; extensions to
the fixed and rolling window follow exactly as in \citet{WeM:98}.

\begin{proof}[Proof of Lemma~\ref{res:a4}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq 
  \Big\lvert \oclt{t} (\nabla f_t^*(\hat\beta_T) - F^*) B^* \Big\rvert
  \sup_t | H_t^* |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_t | H_t^* | \to^p 0$; $\oclt{t} (\nabla
f_t^*(\hat\beta_T) - F^*)$ obeys a \clt\ \citep{Cal:11d} and is
$O_{p^*}(1)$, establishing~\eqref{eq:7}.  The proofs of~\eqref{eq:9}
and~\eqref{eq:10} are similar.
\end{proof}

\begin{lema}\label{res:a3}
  Suppose the conditions of Theorem~\ref{res:3} hold and let
  \[\psi_t^{*}(\beta) = 
  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)}.\]
  Then
  \begin{equation}\label{eq:1}
    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \oclt{t} \psi_{t}^{*}(\hat\beta_T)
    \leq x \Big] - \pr\Big[ \oclt{t} \psi_{t}(\beta_0)
    \leq x \Big] \Big| > \epsilon \Big] \to 0
  \end{equation}
  for all positive $\epsilon$.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a3}]
  Note that both $\psi_t(\beta_0)$ and $\psi_t^*(\hat\beta_T)$ satisfy
  \clt s, (\citealp[Theorem~2]{Jon:97} and
  \citealp[Theorem~1]{Cal:11d}) so it suffices to prove that
  \[ \tfrac{ 1 }{ P } \var^* \Big( \osum{t} \psi_t^*( \hat
  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \osum{t} \psi_t(
  \beta_0 ) \Big) \to^p 0. \]
  I will prove this result for the Circular Block Bootstrap
  \citep{PoR:92}---the proof for other block bootstraps is similar and
  follows as in \cite{Cal:11d}.

@@

  The first term of \eqref{eq:6} can be shown to converge in
  probability to $(1/P) \var \osum{t} \psi_t( \beta_0 )$
  by Theorem 2.2 of \citet{JoD:00}.  Most of the necessary conditions
  hold by assumption and it suffices to prove their condition (2.9)
  holds, namely that
  \begin{equation}\label{eq:2}
    \sup_{\beta \in N} \Bigg\lVert \tfrac{1}{T} \sum_{t=1}^T e^{i \xi t/b} 
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} -
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
    \Bigg\rVert_2 \to 0
  \end{equation}
  for all $i$, $j$, and $\xi$.  Now, for any fixed $\beta \in N$,
  \begin{equation*}
    \tfrac{1}{T} \sum_{t=1}^T \cos( \xi t / b )
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
    \to^p 0
  \end{equation*}
  and
  \begin{equation*}
    \tfrac{1}{T} \sum_{t=1}^T \sin( \xi t / b )
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg)
    \to^p 0
  \end{equation*}
  by a mixingale \lln\ \citep{Dav:93}.\footnote{Remember that \ned\
    processes are also mixingales.  See, for example, \citet[Section
    17.2]{Dav:94}.}  Convergence in $L_2$ for each $\beta \in N$ then
  follows from the existence of the $r$th moment and uniform
  convergence is a consequence of the bounded second derivative of
  $\psi_t$.

@@

\begin{lema}\label{res:a5}
  If the conditions of Theorem~\ref{res:3} hold\footnote{The
    assumptions governing $\hat{\beta}_t^{*}$ are unnecessary.} then
  \begin{equation}
    \oclt{t}
    (f_{t}(\hat{\beta}_{t}) - \E f_{t}(\beta_{0})) \to^d N(0, \Omega),
  \end{equation}
  with $\Omega$ given in \citet[Theorem 2.3.1]{Mcc:00}.
\end{lema}
\begin{proof}[Proof of Lemma~\ref{res:a5}]
  The proof follows exactly as in \citet[Theorem 2.3.1]{Mcc:00}, using
  the previous results in this appendix as substitutes where the
  original proof requires stronger moment or weak dependence
  conditions.
\end{proof}
